\documentclass[letterpaper,notitlepage,11pt]{article}
\usepackage[margin=2cm]{geometry}
\usepackage{color}
\begin{document}
\title{LaTeX Description}
\author{Zakir Alibhai}
\date{\today}
\maketitle
\begin{abstract}
TeX is a typesetting computer program created by Donald Knuth, originally for his magnum opus, The Art of Computer Programming. It takes a "plain" text file and converts it into a high-quality document for printing or on-screen viewing. LaTeX is a macro system built on top of TeX that aims to simplify its use and automate many common formatting tasks. It is the de-facto standard for academic journals and books in several fields, such as mathematics and physics, and provides some of the best typography free software has to offer.
\end{abstract}
\section{Introduction}
\label{Intro}
LaTeX is a computer program used for making articles, books and math formulas look good. LaTeX is well-suited for expressing mathematical formulas on electronic devices in a more human readable format, by showing them in a way similar to how they would be written by hand.
\subsection{Uses}
LaTeX is used for making mathematical formulas for some articles on Wikipedia, in addition to being used within academic circles.
\subsection{Process}
The writer types their article into a plain text document. A plain text document cannot have styled text, like bold or italic. When the writer wants to write styled text, they use special LaTeX commands that start with a backslash. For example, the command for bold text is \textbf{This text is bold}.

After the writer is finished writing the article, they tell LaTeX to read the document. After LaTeX is done, LaTeX makes a file that can be printed. The command \textbf{This text is bold} would print as This text is bold.
I can label before it too like Section \ref{myMethods}


\section{Method}
\label{myMethods}
Here we discuss my methods...

\subsection{History}
LaTeX was first made in the early 1980s by Leslie Lamport at SRI International, who published its first manual in 1986.[1] The current version is LaTeX2e (styled \LaTeXe), which has been active since 1994.[2]

In Sec. ~\ref{myMethods} is is shown how to do a thing.




\end{document}